### 2020-04-18 Thesis-Chapter1-Introduction.tex
Formatting improvements

\newcommand{\principlesstart}{\begin{enumerate}}
\newcommand{\principle}[1]{\item \textbf{#1.}}
\newcommand{\principlesend}{\end{enumerate}}

@@

\principle{Cybersecurity is critical} With current levels of reliance on computer information systems, cybersecurity is
critical to the wellbeing of society. Two important elements of cybersecurity are cryptography and system architecture.
Policy which supports security does not undercut cryptographic integrity or require high-risk architectures.

\principle{Absolute privacy is not an absolute right} Certain rights supersede the legitimate claims of government, but
absolute privacy is not one of them. In some contexts, absolute privacy is proper, and in almost all contexts,
reasonable privacy should be presumed. However, privacy is not an absolute right, and investigators should have access
to some classes of data. Access to these classes of data is important today and will be increasingly important in the
future.

\principle{\Ac{EA} is an inherently complex problem} The factors factors that make \ac{EA} a \ac{wicked-prob} mean that
proposed solutions must be analyzed at many levels. Some these factors are \ac{EA}'s relation to mass surveillance,
potential for abuse, international reception, economic impact, and need for transparency.

\principle{Perfection is not the standard} Wicked policy problems do not have perfect solutions, or even verifiably
optimal solutions, so we cannot use perfection as the standard. To quote the ``insecurity axioms,'' insecurity cannot be
destroyed, only moved around \cite{nrc_schneider_1999}. \Ac{EA}, like all security problems, is a matter of finding the
right balance of risk given the threats under consideration--which includes regulatory action.

>>>>

\newcommand{\principlesstart}{\begin{enumerate}}
\newcommand{\principle}[2]{\item \textbf{#1.} #2}
\newcommand{\principlesend}{\end{enumerate}}

@@

\principle{Cybersecurity is critical}{With current levels of reliance on computer information systems, cybersecurity is
critical to the wellbeing of society. Two important elements of cybersecurity are cryptography and system architecture.
Policy which supports security does not undercut cryptographic integrity or require high-risk architectures.}

\principle{Absolute privacy is not an absolute right}{Certain rights supersede the legitimate claims of government, but
absolute privacy is not one of them. In some contexts, absolute privacy is proper, and in almost all contexts,
reasonable privacy should be presumed. However, privacy is not an absolute right, and investigators should have access
to some classes of data. Access to these classes of data is important today and will be increasingly important in the
future.}

\principle{\Ac{EA} is an inherently complex problem}{The factors factors that make \ac{EA} a \ac{wicked-prob} mean that
proposed solutions must be analyzed at many levels. Some these factors are \ac{EA}'s relation to mass surveillance,
potential for abuse, international reception, economic impact, and need for transparency.}

\principle{Perfection is not the standard}{Wicked policy problems do not have perfect solutions, or even verifiably
optimal solutions, so we cannot use perfection as the standard. To quote the ``insecurity axioms,'' insecurity cannot be
destroyed, only moved around \cite{nrc_schneider_1999}. \Ac{EA}, like all security problems, is a matter of finding the
right balance of risk given the threats under consideration--which includes regulatory action.}

### 2020-04-18 Thesis-Chapter2-Background.tex
Formatting improvements

@@

\newcommand{\lawsstart}{\begin{itemize}}
\newcommand{\law}[4]{ % Year, name, citation, description
    \item #1: \textbf{#2} \cite{#3} \newline
    \parbox{\linewidth}{#4} \newline
}
\newcommand{\lawsend}{\end{itemize}}

@@

% IDEA: go into
%  Wiretap Act (http://www.law.cornell.edu/uscode/usc_sup_01_18_10_I_20_119.html)
%  Stored Communications Act (http://www.law.cornell.edu/uscode/usc_sup_01_18_10_I_20_121.html)
%  Pen Register Act (http://www.law.cornell.edu/uscode/usc_sup_01_18_10_II_20_206.html)
% etc?

@@

    \law{1986}{\acf{CFAA}}{hughes_hr4718_1986}{

% FIXME: is this actually related enough to keep?

Criminalized ``knowingly access[ing] a computer without authorization or exceeding authorized access'' and thereby
violating the confidentiality, integrity, or availability of the system. While presumably intended to target hacking,
the \acs{CFAA} has been used to prosecute a host of crimes, and suffers from dated language;
% --what does it mean to ``access'' a ``computer'' loading a simple webpage may involve dozens of devices--
whether violating the terms of service constitutes ``exceeding authorized access'' remains an open question
\cite{wolff_computer_2016}. Importantly for \ac{EA}, the law includes carve-outs for law enforcement and intelligence
activities.

@@

%     \law{2007}{\acf{PAA}}{mcconnell_s1927_2007}{
%
% Retroactively approved of GWB's warrentless wiretapping policy, a loose intepretation of FISA
% \cite{landau_making_2013}
%
% }

@@

}
% \cite{thompson_2015}

@@

    \law{1997}{Encrypted Communications Privacy Act}{leahy_s376_1997}{

% mix of SE protection and EA guidelines?

    \law{1998}{Encryption Protects the Rights of Individuals from Violation and Abuse in CYberspace (E-PRIVACY) Act}
        {ashcroft_s2067_1998}{

% like above?

    \law{1999}{Encryption for the National Interest Act}{goss_hr2616_1999}{

    \law{1999}{Tax Relief for Responsible Encryption Act}{goss_hr2617_1999}{

% ^^ these two introduced by same rep on same day

@@

    \law{1999}{Enhancement of Privacy and Public Safety in Cyberspace Act}{leahy_s3083_2000}{

@@

\law{2019}{Technology in Criminal Justice Act}{demings_hr5227_2019}{

% pfefferkorn_2019
% And in fact, there’s already proposed legislation based on CSIS’s recommendations: the Technology in Criminal Justice
% Act of 2019, introduced in the House last month by a bipartisan group of co-sponsors led by Rep. Val Demings of Florida.
% The bill seeks to close the resource, training, and information-sharing gap for digital evidence, and to improve the
% frayed relationship between law enforcement and technology companies. Notably absent from the bill is any language that
% would roll back the CALEA compromise or mandate encryption backdoors. To be clear, I’m not advocating for or against
% Rep. Demings’ bill. I just want to point out that it offers an alternative to whatever backdoor nightmare the Senate
% Judiciary Committee is surely drafting up right now.

>>>>

% IDEA: Create an appendix to go into greater detail?
% Could go into these, as well as the commented-out ones below
%  Wiretap Act (http://www.law.cornell.edu/uscode/usc_sup_01_18_10_I_20_119.html)
%  Stored Communications Act (http://www.law.cornell.edu/uscode/usc_sup_01_18_10_I_20_121.html)
%  Pen Register Act (http://www.law.cornell.edu/uscode/usc_sup_01_18_10_II_20_206.html)

@@

\newcommand{\lawsstart}{\begin{itemize}}
\newcommand{\law}[4]{ % Year, name, citation, description
    \item #1: \textbf{#2} \cite{#3}

    \vspace{0.5\baselineskip} \parbox{\linewidth}{#4} \vspace{0.5\baselineskip}
}
\newcommand{\lawsend}{\end{itemize}}

@@

@@

%     \law{1986}{\acf{CFAA}}{hughes_hr4718_1986}{
% Criminalized ``knowingly access[ing] a computer without authorization or exceeding authorized access'' and thereby
% violating the confidentiality, integrity, or availability of the system. While presumably intended to target hacking,
% the \acs{CFAA} has been used to prosecute a host of crimes, and suffers from dated language;
% % --what does it mean to ``access'' a ``computer'' loading a simple webpage may involve dozens of devices--
% whether violating the terms of service constitutes ``exceeding authorized access'' remains an open question
% \cite{wolff_computer_2016}. Importantly for \ac{EA}, the law includes carve-outs for law enforcement and intelligence
% activities.
% }

@@

%     \law{2007}{\acf{PAA}}{mcconnell_s1927_2007}{
% Retroactively approved of GWB's warrantless wiretapping policy, a loose interpretation of FISA
% \cite{landau_making_2013}.
% }

@@

@@

%     \law{1997}{Encrypted Communications Privacy Act}{leahy_s376_1997}{
% % mix of SE protection and EA guidelines?
% }

%     \law{1998}{Encryption Protects the Rights of Individuals from Violation and Abuse in CYberspace (E-PRIVACY) Act}
%         {ashcroft_s2067_1998}{
% % like above?
% }

%     \law{1999}{Encryption for the National Interest Act}{goss_hr2616_1999}{
% }

%     \law{1999}{Tax Relief for Responsible Encryption Act}{goss_hr2617_1999}{
% % ^^ these two introduced by same rep on same day
% }

@@

    \law{2000}{Enhancement of Privacy and Public Safety in Cyberspace Act}{leahy_s3083_2000}{

@@

% \law{2019}{Technology in Criminal Justice Act}{demings_hr5227_2019}{
% % pfefferkorn_2019
% % And in fact, there’s already proposed legislation based on CSIS’s recommendations: the Technology in Criminal Justice
% % Act of 2019, introduced in the House last month by a bipartisan group of co-sponsors led by Rep. Val Demings of Florida.
% % The bill seeks to close the resource, training, and information-sharing gap for digital evidence, and to improve the
% % frayed relationship between law enforcement and technology companies. Notably absent from the bill is any language that
% % would roll back the CALEA compromise or mandate encryption backdoors. To be clear, I’m not advocating for or against
% % Rep. Demings’ bill. I just want to point out that it offers an alternative to whatever backdoor nightmare the Senate
% % Judiciary Committee is surely drafting up right now.
% }
